---
title: "R Notebook"
output: html_notebook
---

```{r}
## Load up some packages we will be using for Decision Trees
library(caTools)
library(rpart)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(caret) 
library(tidyverse)
```


```{r}
fight_data <- read.csv("data/fight_train.csv")
```

1. Split your data using a 2/3 training and 1/3 test split
```{r}
fight_data <- fight_data %>%
  select(colnames(fight_data_final)[-43], Winner)

set.seed(5)
d_sample <- sample.split(fight_data$Winner,SplitRatio=0.67)
fight_train <- subset(fight_data,d_sample==TRUE)
fight_test <- subset(fight_data,d_sample==FALSE)
```


```{r}
#fight_data_fit <- fight_data %>%
#  select(-c(X, location, R_Stance, B_Stance, Referee, date, Winner, weight_class, R_fighter, B_fighter))
```


2. Create a full decision tree with your Training Data. Outcome is your class label and all other variables can be used as attributes of your model
```{r}

fight_tree <- rpart(Winner ~ ., data=fight_train, method = "class",
                     parms = list(split = 'information'),cp=-1)
fight_tree
```


3. Create the graphic of the decision tree you just made
```{r}
fancyRpartPlot(fight_tree)
```



4. Test the Accuracy of this model of with Test Data
```{r}
pred <-predict(fight_tree,fight_test,type = "class")
conf <- table(pred,fight_test$Winner)
confusionMatrix(conf)
confusionMatrix(conf)$byClass
```


5. Create a post-pruned decision tree with your Training Data with the graphic. Use 
```{r}
printcp(fight_tree)
plotcp(fight_tree)
cp = fight_tree$cptable[which.min(fight_tree$cptable[,"xerror"]),"CP"]
```

## Fit the Model
```{r}
post_fight_tree <- rpart(Winner ~ ., data=fight_train, method = "class",
             parms = list(split = 'information'),cp=cp)
post_fight_tree
```

```{r}
fancyRpartPlot(post_fight_tree)
```

6. Test the accuracy of your post-pruned tree with the Test Data. Did we improve the fit of the model by pruning?


## Make the Predictions
```{r}
post_pred<-predict(post_fight_tree,fight_test,type = "class")
```

## Measures of Fit
```{r}
post_conf <- table(post_pred,fight_test$Winner)
confusionMatrix(post_conf)
confusionMatrix(post_conf)$byClass
```
